Bird beak's elaboration and innovation

### 2022-05-20 Analysis/06-Figure3_with_correlations.Rmd
Added contour estimations test

    ## Adding contours
    if(!is.null(contour)) {
        ## Select the right contour data
        contour_data <- contour[match(rownames(plot_data), names(contour))]        
        ## Calculate the contour
        contour_z <- MASS::kde2d(contour_data/max(contour_data)*max(plot_data$x), contour_data/max(contour_data)*max(plot_data$y), n = 50)

        contour_z <- matrix(0, nrow = length(contour_data), ncol = length(contour_data))
        diag(contour_z) <-  contour_data
        # contour_z <- outer(contour_data/max(contour_data)*max(plot_data$x), contour_data/max(contour_data)*max(plot_data$y))

        ## Adding the contour in the background
        contour(contour_z, lwd = 1, add = TRUE, col = hcl.colors(12, palette = "viridis"), labels = pretty(contour_data))
    }

    # ## col test for contour
    # color.gradient <- function(x, colors=c("red","yellow","green"), colsteps=100) {
    #     return( colorRampPalette(colors) (colsteps) [ findInterval(x, seq(min(x),max(x), length.out=colsteps)) ] )
    # }

    ## Plot the points
    points(plot_data$x, plot_data$y, pch = 19, cex = pt.cex, col = plot_data$col)
    # points(plot_data$x, plot_data$y, pch = 19, cex = pt.cex, col = color.gradient(contour_data))

@@

for(i in 1:8) {
    par(mar = c(2,2.5,2,1.5))
    one.plot.correlations(super_phylo_cor[[i]], col.sub = col_subs[[i]], legend.pos = legends_pos[i], ID = i, pt.cex = 0.5, legend.cex = 2/3, legend_counter = legend_counter, contour = NULL, with.quadrant = TRUE)
}

>>>>

    ## Adding contours
    if(!is.null(contour)) {

        ## Get the contour data
        contour_data <- contour[match(rownames(plot_data), names(contour))]

        ## This function is copied/modified from ContourFunctions
        estimate.contour <- function(x, y, z) {
            X <- data.frame(x, y, z)
            ## Set the model for estiamtions
            lfmod <- locfit::locfit(z ~ x + y, data=X, family=family)
            ## Predicting function
            pred.func <- function(xx) {
              predict(lfmod, data.frame(x=xx[,1], y=xx[,2]))
            }
            ## Calculating the contour matrix
            return(ContourFunctions::eval_over_grid_with_batch(x = seq(min(x), max(x), length.out = 100),
                                                               y = seq(min(y), max(y), length.out = 100),
                                                               fn = pred.func,
                                                               batchmax = 500))
        }

        ## Plot the estimated contour
        contour(estimate.contour(x = plot_data$x, y = plot_data$y, z = unname(contour_data)),
                lwd = 1, add = TRUE,
                col = hcl.colors(12, palette = "viridis"),
                labels = pretty(contour_data))

        ## TODO: scale and rescale the data (so that it's beyond c(0,1))
        ## TODO: check bug with Strisores (i = 7)

        ## TESTING
        # ## col test for contour
        # color.gradient <- function(x, colors=c("red","yellow","green"), colsteps=100) {
        #     return( colorRampPalette(colors) (colsteps) [ findInterval(x, seq(min(x),max(x), length.out=colsteps)) ] )
        # }

        # plot(NULL, xlim = range(plot_data$x), ylim = range(plot_data$y), xlab = "", ylab = "", main = strsplit(cor.results$main, split = ":")[[1]][1])
        # points(plot_data$x, plot_data$y, pch = 19, cex = 1, col = color.gradient(contour_data))
    }

    ## Plot the points
    points(plot_data$x, plot_data$y, pch = 19, cex = pt.cex, col = plot_data$col)

@@

for(i in 1:8) {
    par(mar = c(2,2.5,2,1.5))
    one.plot.correlations(super_phylo_cor[[i]], col.sub = col_subs[[i]], legend.pos = legends_pos[i], ID = i, pt.cex = 0.5, legend.cex = 2/3, legend_counter = legend_counter, contour = centroids, with.quadrant = TRUE)
}
